\emph{Gaia} DR2 adds clues for dynamical ejection of a $\sim$$150\,M_\odot$ star

### 2018-06-06 VFTS682_APJL.tex
getting yellow warning from ApJL word count: excess is ~500 words

Based on our results, we tentatively claim that VFTS682 is the most massive
runaway known to date, with a peculiar three-dimensional speed of
$44\pm21\,\kms$. This result will need to be revisited as updated
astrometric parameters from future \emph{Gaia} data releases become
available. If this result will be confirmed, it means that isolated star formation is
\emph{not} required to explain this star. Its proper motion suggests that it was ejected from the cluster R136
$0.9\pm0.6$\,Myr ago. Because of the exceptionally large mass
of this star, this raises the question of which stars must populate
the core of the cluster.

Dynamical ejections due to N-body interactions typically (although, not necessarily) eject the least
massive star among those interacting \cite[e.g.,][]{banerjee:12}. This means that, just
based on the kinematic properties of VFTS682, we would expect several
stars with initial masses larger than $\sim$$150\,M_\odot$ in the
cluster R136.
This is consistent with the detection
of extremely massive stars by \cite{crowther:10} in the core of the
cluster. % The projected rotational equatorial
% velocity\footnote{However, the determination of the rotational
%   velocity for stars showing lines in emission is complicated by the optically thick wind screening the surface of the star, and should be
%   considered with caution.} of VFTS682
% reported by \cite{schneider:18} is $v\sin(i)<200\,\kms$, which is in
% line with the average rotation rate of massive stars in the region
% \citep[][]{ramirez-agudelo:15}. This suggests that VFTS682 (i) has not
% experienced rotationally induced chemically homogeneous evolution
% \citep[][]{maeder:00,demink:09}, and (ii) it has not
% accreted mass from or merged with a binary companion, nor will it, since the multi-epoch
% data of the VFTS survey rule out the presence of a close companion at the
% present day. Moreover,

The spectral type of VFTS682
\citep[WNh5,][]{bestenlehner:11} is the same as R136a1-a3, i.e.~the
three most massive stars detected in the core of the cluster by
\cite{dekoter:97,crowther:10,crowther:16}, with an astonishing similarity in particular with
the spectrum of R136a3. Therefore, the isolation of
VFTS682 makes it an ideal target to constrain the stellar physics of
stars with masses well above $\sim$$100\,M_\odot$ while avoiding
crowding issues. %  : its isolation makes
% it an easier target for observations compared to the similar stars
% present in the crowded core of R136.

\citet{banerjee:12} used N-body simulations of fully segregated
clusters with all massive stars in binaries to suggest that VFTS682
was ejected from R136. They
demonstrated that the cluster potential does not significantly change
the velocity of the star after the ejection. In their
model, they relied on (dynamically driven) stellar mergers to explain the high masses of
VFTS682 and the massive members of R136. While it is not possible to
robustly exclude that VFTS682 is itself a merger, its spectrum does not show any of the obvious signatures
like fast rotation, which however could have already slowed down
because of the wind angular momentum losses during and after the
merger.

@@

\bibliographystyle{aa}
\bibliography{bibliography/vfts682}

\begin{acknowledgements}
  \small
  We are grateful to S.~Torres, M.~C.~Ramirez-Tannus,
  and C.~J.~Evans for help and discussions. SdM has received funding under the European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC) (Grant agreement No. 715063). VHB acknowledges support from the NRC-Canada Plaskett Fellowship. This work has made use of data from the ESA space mission \emph{Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the \emph{Gaia} Data Processing and Analysis Consortium (DPAC, \url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \emph{Gaia} Multilateral Agreement. The background image of \Figref{fig:main} is based on observations
  made with ESO Telescopes at the La Silla Observatory under programme
  ID 076.C-0888, processed and released by the ESO VOS/ADP group.
  This research made use of APLpy, an open-source plotting package for Python \citep[][]{robitaille:12}.
\end{acknowledgements}

>>>>

Based on our results, we tentatively claim that VFTS682 is the most massive
runaway known to date, with a peculiar three-dimensional speed of
$44\pm21\,\kms$. Due to the large error bars, this result will need
to be revisited with future astrometric data. % to be revisited as updated
% astrometric parameters from future \emph{Gaia} data releases become
% available.
If confirmed, it means that isolated star formation is
\emph{not} required to explain the isolation of VFTS682. Its proper motion suggests that it was ejected from the cluster R136
$0.9\pm0.6$\,Myr ago. Because of the exceptionally large mass
of this star, this raises the question of which stars must populate
the core of the cluster.

Dynamical ejections due to N-body interactions typically (although, not necessarily) eject the least
massive star among those interacting \cite[e.g.,][]{banerjee:12}. This means that, just
based on the kinematic properties of VFTS682, we would expect several
stars with initial masses larger than $\sim$$150\,M_\odot$ in the
cluster R136.
This is consistent with the detection
of extremely massive stars in the core of the
cluster. % The projected rotational equatorial
% velocity\footnote{However, the determination of the rotational
%   velocity for stars showing lines in emission is complicated by the optically thick wind screening the surface of the star, and should be
%   considered with caution.} of VFTS682
% reported by \cite{schneider:18} is $v\sin(i)<200\,\kms$, which is in
% line with the average rotation rate of massive stars in the region
% \citep[][]{ramirez-agudelo:15}. This suggests that VFTS682 (i) has not
% experienced rotationally induced chemically homogeneous evolution
% \citep[][]{maeder:00,demink:09}, and (ii) it has not
% accreted mass from or merged with a binary companion, nor will it, since the multi-epoch
% data of the VFTS survey rule out the presence of a close companion at the
% present day. Moreover,

The spectral type of VFTS682
\citep[WNh5,][]{bestenlehner:11} is the same as R136a1-a3, i.e.~the
three most massive stars detected in the core of the cluster%  by
% \cite{dekoter:97,crowther:10,crowther:16}
, with an astonishing similarity in particular with
the spectrum of R136a3. Therefore, the isolation of
VFTS682 makes it an ideal target to constrain the stellar physics of
stars with masses well above $\sim$$100\,M_\odot$ while avoiding
crowding issues. %  : its isolation makes
% it an easier target for observations compared to the similar stars
% present in the crowded core of R136.

\citet{banerjee:12} used N-body simulations of fully segregated
clusters with all massive stars in binaries to suggest that VFTS682
was ejected from R136. They
demonstrated that the cluster potential does not significantly change
the velocity of the star after the ejection. In their
model, they relied on (dynamically driven) stellar mergers to explain the high masses of
VFTS682 and the massive members of R136.%  While it is not possible to
% robustly exclude that VFTS682 is itself a merger, its spectrum does not show any of the obvious signatures
% like fast rotation, which however could have already slowed down
% because of the wind angular momentum losses during and after the
% merger.

@@

% \bibliographystyle{aa}
% \bibliography{bibliography/vfts682}
\begin{thebibliography}{}
\makeatletter
\relax
\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
  {\mn@doi@[]}}
\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
  \endgroup}
\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
  {dblp:#1}}
\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}

\bibitem[\protect\citeauthoryear{{Banerjee}, {Kroupa}  \& {Oh}}{{Banerjee}
  et~al.}{2012}]{banerjee:12}
{Banerjee} S.,  {Kroupa} P.,   {Oh} S.,  2012, \mn@doi [\apj]
  {10.1088/0004-637X/746/1/15}, \href
  {http://adsabs.harvard.edu/abs/2012ApJ...746...15B} {746, 15}

\bibitem[\protect\citeauthoryear{{Bate}}{{Bate}}{2009}]{bate:09}
{Bate} M.~R.,  2009, \mn@doi [\mnras] {10.1111/j.1365-2966.2008.14106.x}, \href
  {http://adsabs.harvard.edu/abs/2009MNRAS.392..590B} {392, 590}

\bibitem[\protect\citeauthoryear{{Bestenlehner} et~al.,}{{Bestenlehner}
  et~al.}{2011}]{bestenlehner:11}
{Bestenlehner} J.~M.,  et~al., 2011, \mn@doi [\aap]
  {10.1051/0004-6361/201117043}, \href
  {http://adsabs.harvard.edu/abs/2011A\%26A...530L..14B} {530, L14}

\bibitem[\protect\citeauthoryear{{Blaauw}}{{Blaauw}}{1961}]{blaauw:61}
{Blaauw} A.,  1961, \bain, \href
  {http://adsabs.harvard.edu/abs/1961BAN....15..265B} {15, 265}

\bibitem[\protect\citeauthoryear{{Bressert} et~al.,}{{Bressert}
  et~al.}{2012}]{bressert:12}
{Bressert} E.,  et~al., 2012, \mn@doi [\aap] {10.1051/0004-6361/201117247},
  \href {http://adsabs.harvard.edu/abs/2012A\%26A...542A..49B} {542, A49}

\bibitem[\protect\citeauthoryear{{Brott} et~al.,}{{Brott}
  et~al.}{2011}]{brott:11}
{Brott} I.,  et~al., 2011, \mn@doi [\aap] {10.1051/0004-6361/201016113}, \href
  {http://adsabs.harvard.edu/abs/2011A\%26A...530A.115B} {530, A115}

\bibitem[\protect\citeauthoryear{{Crowther}, {Schnurr}, {Hirschi}, {Yusof},
  {Parker}, {Goodwin}  \& {Kassim}}{{Crowther} et~al.}{2010}]{crowther:10}
{Crowther} P.~A.,  {Schnurr} O.,  {Hirschi} R.,  {Yusof} N.,  {Parker} R.~J.,
  {Goodwin} S.~P.,   {Kassim} H.~A.,  2010, \mn@doi [\mnras]
  {10.1111/j.1365-2966.2010.17167.x}, \href
  {http://adsabs.harvard.edu/abs/2010MNRAS.408..731C} {408, 731}

\bibitem[\protect\citeauthoryear{{Crowther} et~al.,}{{Crowther}
  et~al.}{2016}]{crowther:16}
{Crowther} P.~A.,  et~al., 2016, \mn@doi [\mnras] {10.1093/mnras/stw273}, \href
  {http://adsabs.harvard.edu/abs/2016MNRAS.458..624C} {458, 624}

\bibitem[\protect\citeauthoryear{{Davidson}, {Humphreys}  \& {Weis}}{{Davidson}
  et~al.}{2016}]{davidson:16}
{Davidson} K.,  {Humphreys} R.~M.,   {Weis} K.,  2016, arXiv:1608.02007, \href
  {http://adsabs.harvard.edu/abs/2016arXiv160802007D} {}

\bibitem[\protect\citeauthoryear{{Evans} et~al.,}{{Evans}
  et~al.}{2010}]{evans:10}
{Evans} C.~J.,  et~al., 2010, \mn@doi [\apjl] {10.1088/2041-8205/715/2/L74},
  \href {http://adsabs.harvard.edu/abs/2010ApJ...715L..74E} {715, L74}

\bibitem[\protect\citeauthoryear{{Evans} et~al.,}{{Evans}
  et~al.}{2011}]{evans:11}
{Evans} C.~J.,  et~al., 2011, \mn@doi [\aap] {10.1051/0004-6361/201116782},
  \href {http://adsabs.harvard.edu/abs/2011A\%26A...530A.108E} {530, A108}

\bibitem[\protect\citeauthoryear{{Fujii} \& {Portegies Zwart}}{{Fujii} \&
  {Portegies Zwart}}{2011}]{fujii:11}
{Fujii} M.~S.,  {Portegies Zwart} S.,  2011, \mn@doi [Science]
  {10.1126/science.1211927}, \href
  {http://adsabs.harvard.edu/abs/2011Sci...334.1380F} {334, 1380}

\bibitem[\protect\citeauthoryear{{Gaia Collaboration} et~al.,}{{Gaia
  Collaboration} et~al.}{2016}]{gaia:16}
{Gaia Collaboration} et~al., 2016, \mn@doi [\aap]
  {10.1051/0004-6361/201629272}, \href
  {http://adsabs.harvard.edu/abs/2016A\%26A...595A...1G} {595, A1}

\bibitem[\protect\citeauthoryear{{Gaia Collaboration}, {Brown}, {Vallenari},
  {Prusti}, {de Bruijne}, {Babusiaux}  \& {Bailer-Jones}}{{Gaia Collaboration}
  et~al.}{2018}]{brown:18}
{Gaia Collaboration} {Brown} A.~G.~A.,  {Vallenari} A.,  {Prusti} T.,  {de
  Bruijne} J.~H.~J.,  {Babusiaux} C.,   {Bailer-Jones} C.~A.~L.,  2018,
  ArXiv:1804.09365, \href {http://adsabs.harvard.edu/abs/2018arXiv180409365G}
  {}

\bibitem[\protect\citeauthoryear{{Gruendl} \& {Chu}}{{Gruendl} \&
  {Chu}}{2009}]{gruendl:09}
{Gruendl} R.~A.,  {Chu} Y.-H.,  2009, \mn@doi [\apjs]
  {10.1088/0067-0049/184/1/172}, \href
  {http://adsabs.harvard.edu/abs/2009ApJS..184..172G} {184, 172}

\bibitem[\protect\citeauthoryear{{Gvaramadze}, {Weidner}, {Kroupa}  \&
  {Pflamm-Altenburg}}{{Gvaramadze} et~al.}{2012}]{gvaramadze:12}
{Gvaramadze} V.~V.,  {Weidner} C.,  {Kroupa} P.,   {Pflamm-Altenburg} J.,
  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21452.x}, \href
  {http://adsabs.harvard.edu/abs/2012MNRAS.424.3037G} {424, 3037}

\bibitem[\protect\citeauthoryear{{Hogg}}{{Hogg}}{2018}]{hogg:18}
{Hogg} D.~W.,  2018, ArXiv:1804.07766, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180407766H} {}

\bibitem[\protect\citeauthoryear{{Humphreys}, {Weis}, {Davidson}  \&
  {Gordon}}{{Humphreys} et~al.}{2016}]{humphreys:16}
{Humphreys} R.~M.,  {Weis} K.,  {Davidson} K.,   {Gordon} M.~S.,  2016, \mn@doi
  [\apj] {10.3847/0004-637X/825/1/64}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...825...64H} {825, 64}

\bibitem[\protect\citeauthoryear{{K{\"o}hler} et~al.,}{{K{\"o}hler}
  et~al.}{2015}]{kohler:15}
{K{\"o}hler} K.,  et~al., 2015, \mn@doi [\aap] {10.1051/0004-6361/201424356},
  \href {http://adsabs.harvard.edu/abs/2015A\%26A...573A..71K} {573, A71}

\bibitem[\protect\citeauthoryear{{Kuiper}, {Yorke}  \& {Turner}}{{Kuiper}
  et~al.}{2015}]{kuiper:15}
{Kuiper} R.,  {Yorke} H.~W.,   {Turner} N.~J.,  2015, \mn@doi [\apj]
  {10.1088/0004-637X/800/2/86}, \href
  {http://adsabs.harvard.edu/abs/2015ApJ...800...86K} {800, 86}

\bibitem[\protect\citeauthoryear{{Lada} \& {Lada}}{{Lada} \&
  {Lada}}{2003}]{lada:03}
{Lada} C.~J.,  {Lada} E.~A.,  2003, \mn@doi [\araa]
  {10.1146/annurev.astro.41.011802.094844}, \href
  {http://adsabs.harvard.edu/abs/2003ARA\%26A..41...57L} {41, 57}

\bibitem[\protect\citeauthoryear{{Lamb}, {Oey}, {Segura-Cox}, {Graus},
  {Kiminki}, {Golden-Marx}  \& {Parker}}{{Lamb} et~al.}{2016}]{lamb:16}
{Lamb} J.~B.,  {Oey} M.~S.,  {Segura-Cox} D.~M.,  {Graus} A.~S.,  {Kiminki}
  D.~C.,  {Golden-Marx} J.~B.,   {Parker} J.~W.,  2016, \mn@doi [\apj]
  {10.3847/0004-637X/817/2/113}, \href
  {http://adsabs.harvard.edu/abs/2016ApJ...817..113L} {817, 113}

\bibitem[\protect\citeauthoryear{{Langer}, {Norman}, {de Koter}, {Vink},
  {Cantiello}  \& {Yoon}}{{Langer} et~al.}{2007}]{langer:07}
{Langer} N.,  {Norman} C.~A.,  {de Koter} A.,  {Vink} J.~S.,  {Cantiello} M.,
  {Yoon} S.-C.,  2007, \mn@doi [\aap] {10.1051/0004-6361:20078482}, \href
  {http://adsabs.harvard.edu/abs/2007A\%26A...475L..19L} {475, L19}

\bibitem[\protect\citeauthoryear{{Lennon} et~al.,}{{Lennon}
  et~al.}{2018}]{lennon:18}
{Lennon} D.~J.,  et~al., 2018, ArXiv:1805.08277, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180508277L} {}

\bibitem[\protect\citeauthoryear{{Lindegren} et~al.,}{{Lindegren}
  et~al.}{2018}]{lindengren:18}
{Lindegren} L.,  et~al., 2018, ArXiv:1804.09366, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180409366L} {}

\bibitem[\protect\citeauthoryear{{Maeder} \& {Meynet}}{{Maeder} \&
  {Meynet}}{2000}]{maeder:00}
{Maeder} A.,  {Meynet} G.,  2000, \aap, \href
  {http://adsabs.harvard.edu/abs/2000A\%26A...361..159M} {361, 159}

\bibitem[\protect\citeauthoryear{{Oh} \& {Kroupa}}{{Oh} \&
  {Kroupa}}{2016}]{oh:16}
{Oh} S.,  {Kroupa} P.,  2016, \mn@doi [\aap] {10.1051/0004-6361/201628233},
  \href {http://adsabs.harvard.edu/abs/2016A\%26A...590A.107O} {590, A107}

% \bibitem[\protect\citeauthoryear{{Parker}}{{Parker}}{1993}]{parker:93}
% {Parker} J.~W.,  1993, \mn@doi [\aj] {10.1086/116661}, \href
%   {http://adsabs.harvard.edu/abs/1993AJ....106..560P} {106, 560}

\bibitem[\protect\citeauthoryear{{Pietrzy{\'n}ski} et~al.,}{{Pietrzy{\'n}ski}
  et~al.}{2013}]{pietrzynski:13}
{Pietrzy{\'n}ski} G.,  et~al., 2013, \mn@doi [\nat] {10.1038/nature11878},
  \href {http://adsabs.harvard.edu/abs/2013Natur.495...76P} {495, 76}

\bibitem[\protect\citeauthoryear{{Platais}, {van der Marel}, {Lennon},
  {Anderson}, {Bellini}, {Sabbi}, {Sana}  \& {Bedin}}{{Platais}
  et~al.}{2015}]{platais:15}
{Platais} I.,  {van der Marel} R.~P.,  {Lennon} D.~J.,  {Anderson} J.,
  {Bellini} A.,  {Sabbi} E.,  {Sana} H.,   {Bedin} L.~R.,  2015, \mn@doi [\aj]
  {10.1088/0004-6256/150/3/89}, \href
  {http://adsabs.harvard.edu/abs/2015AJ....150...89P} {150, 89}

\bibitem[\protect\citeauthoryear{{Platais} et~al.,}{{Platais}
  et~al.}{2018}]{platais:18}
{Platais} I.,  et~al., 2018, ArXiv:1804.08678, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180408678P} {}

\bibitem[\protect\citeauthoryear{{Poveda}, {Ruiz}  \& {Allen}}{{Poveda}
  et~al.}{1967}]{poveda:67}
{Poveda} A.,  {Ruiz} J.,   {Allen} C.,  1967, Boletin de los Observatorios
  Tonantzintla y Tacubaya, \href
  {http://adsabs.harvard.edu/abs/1967BOTT....4...86P} {4, 86}

\bibitem[\protect\citeauthoryear{{Rakavy} \& {Shaviv}}{{Rakavy} \&
  {Shaviv}}{1967}]{rakavy:67}
{Rakavy} G.,  {Shaviv} G.,  1967, \mn@doi [\apj] {10.1086/149204}, \href
  {http://adsabs.harvard.edu/abs/1967ApJ...148..803R} {148, 803}

\bibitem[\protect\citeauthoryear{{Ram{\'{\i}}rez-Agudelo}
  et~al.,}{{Ram{\'{\i}}rez-Agudelo} et~al.}{2015}]{ramirez-agudelo:15}
{Ram{\'{\i}}rez-Agudelo} O.~H.,  et~al., 2015, \mn@doi [\aap]
  {10.1051/0004-6361/201425424}, \href
  {http://adsabs.harvard.edu/abs/2015A\%26A...580A..92R} {580, A92}

\bibitem[\protect\citeauthoryear{{Renzo} et~al.,}{{Renzo}
  et~al.}{2018}]{renzo:18}
{Renzo} M.,  et~al., 2018, ArXiv:1804.09164, \href
  {http://adsabs.harvard.edu/abs/2018arXiv180409164R} {}

\bibitem[\protect\citeauthoryear{{Robitaille} \& {Bressert}}{{Robitaille} \&
  {Bressert}}{2012}]{robitaille:12}
{Robitaille} T.,  {Bressert} E.,  2012, {APLpy: Astronomical Plotting Library
  in Python}, Astrophysics Source Code Library (\mn@eprint {ascl} {1208.017})

\bibitem[\protect\citeauthoryear{{Rosen}, {Krumholz}, {McKee}  \&
  {Klein}}{{Rosen} et~al.}{2016}]{rosen:16}
{Rosen} A.~L.,  {Krumholz} M.~R.,  {McKee} C.~F.,   {Klein} R.~I.,  2016,
  \mn@doi [\mnras] {10.1093/mnras/stw2153}, \href
  {http://adsabs.harvard.edu/abs/2016MNRAS.463.2553R} {463, 2553}

\bibitem[\protect\citeauthoryear{{Rubio-D{\'{\i}}ez}, {Najarro},
  {Garc{\'{\i}}a}  \& {Sundqvist}}{{Rubio-D{\'{\i}}ez}
  et~al.}{2017}]{rubio-diez:17}
{Rubio-D{\'{\i}}ez} M.~M.,  {Najarro} F.,  {Garc{\'{\i}}a} M.,   {Sundqvist}
  J.~O.,  2017, in {Eldridge} J.~J.,  {Bray} J.~C.,  {McClelland} L.~A.~S.,
  {Xiao} L.,  eds,  IAU Symposium Vol. 329, The Lives and Death-Throes of
  Massive Stars. pp 131--135, \mn@doi{10.1017/S1743921317002447}

\bibitem[\protect\citeauthoryear{{Sabbi} et~al.,}{{Sabbi}
  et~al.}{2012}]{sabbi:12}
{Sabbi} E.,  et~al., 2012, \mn@doi [\apjl] {10.1088/2041-8205/754/2/L37}, \href
  {http://adsabs.harvard.edu/abs/2012ApJ...754L..37S} {754, L37}

\bibitem[\protect\citeauthoryear{{Sana}, {Ram{\'{\i}}rez-Tannus}, {de Koter},
  {Kaper}, {Tramper}  \& {Bik}}{{Sana} et~al.}{2017}]{sana:17}
{Sana} H.,  {Ram{\'{\i}}rez-Tannus} M.~C.,  {de Koter} A.,  {Kaper} L.,
  {Tramper} F.,   {Bik} A.,  2017, \mn@doi [\aap]
  {10.1051/0004-6361/201630087}, \href
  {http://adsabs.harvard.edu/abs/2017A\%26A...599L...9S} {599, L9}

\bibitem[\protect\citeauthoryear{{Schneider}, {Castro}, {Fossati}, {Langer}  \&
  {de Koter}}{{Schneider} et~al.}{2017}]{schneider:17}
{Schneider} F.~R.~N.,  {Castro} N.,  {Fossati} L.,  {Langer} N.,   {de Koter}
  A.,  2017, \mn@doi [\aap] {10.1051/0004-6361/201628409}, \href
  {http://adsabs.harvard.edu/abs/2017A\%26A...598A..60S} {598, A60}

\bibitem[\protect\citeauthoryear{{Schneider} et~al.,}{{Schneider}
  et~al.}{2018}]{schneider:18}
{Schneider} F.~R.~N.,  et~al., 2018, \mn@doi [Science]
  {10.1126/science.aan0106}, \href
  {http://adsabs.harvard.edu/abs/2018Sci...359...69S} {359, 69}

\bibitem[\protect\citeauthoryear{{Smith}}{{Smith}}{2016}]{smith:16}
{Smith} N.,  2016, \mn@doi [\mnras] {10.1093/mnras/stw1533}, \href
  {http://adsabs.harvard.edu/abs/2016MNRAS.461.3353S} {461, 3353}

\bibitem[\protect\citeauthoryear{{Smith} \& {Tombleson}}{{Smith} \&
  {Tombleson}}{2015}]{smith:15}
{Smith} N.,  {Tombleson} R.,  2015, \mn@doi [\mnras] {10.1093/mnras/stu2430},
  \href {http://adsabs.harvard.edu/abs/2015MNRAS.447..598S} {447, 598}

\bibitem[\protect\citeauthoryear{{Udalski} et~al.,}{{Udalski}
  et~al.}{2008}]{udalski:08}
{Udalski} A.,  et~al., 2008, \actaa, \href
  {http://adsabs.harvard.edu/abs/2008AcA....58..329U} {58, 329}

\bibitem[\protect\citeauthoryear{{Ward} \& {Kruijssen}}{{Ward} \&
  {Kruijssen}}{2018}]{ward:18}
{Ward} J.~L.,  {Kruijssen} J.~M.~D.,  2018, \mn@doi [\mnras]
  {10.1093/mnras/sty117}, \href
  {http://adsabs.harvard.edu/abs/2018MNRAS.475.5659W} {475, 5659}

\bibitem[\protect\citeauthoryear{{Zapartas} et~al.,}{{Zapartas}
  et~al.}{2017}]{zapartas:17}
{Zapartas} E.,  et~al., 2017, \mn@doi [\aap] {10.1051/0004-6361/201629685},
  \href {http://adsabs.harvard.edu/abs/2017A\%26A...601A..29Z} {601, A29}

\bibitem[\protect\citeauthoryear{{Zinnecker} \& {Yorke}}{{Zinnecker} \&
  {Yorke}}{2007}]{zinnecker:07}
{Zinnecker} H.,  {Yorke} H.~W.,  2007, \mn@doi [\araa]
  {10.1146/annurev.astro.44.051905.092549}, \href
  {http://adsabs.harvard.edu/abs/2007ARA\%26A..45..481Z} {45, 481}

\bibitem[\protect\citeauthoryear{{Zwicky}}{{Zwicky}}{1957}]{zwicky:57}
{Zwicky} F.,  1957, \zap, \href
  {http://adsabs.harvard.edu/abs/1957ZA.....44...64Z} {44, 64}

\bibitem[\protect\citeauthoryear{{de Koter}, {Heap}  \& {Hubeny}}{{de Koter}
  et~al.}{1997}]{dekoter:97}
{de Koter} A.,  {Heap} S.~R.,   {Hubeny} I.,  1997, \mn@doi [\apj]
  {10.1086/303736}, \href {http://adsabs.harvard.edu/abs/1997ApJ...477..792D}
  {477, 792}

\bibitem[\protect\citeauthoryear{{de Mink}, {Cantiello}, {Langer}, {Pols},
  {Brott}  \& {Yoon}}{{de Mink} et~al.}{2009}]{demink:09}
{de Mink} S.~E.,  {Cantiello} M.,  {Langer} N.,  {Pols} O.~R.,  {Brott} I.,
  {Yoon} S.-C.,  2009, \mn@doi [\aap] {10.1051/0004-6361/200811439}, \href
  {http://adsabs.harvard.edu/abs/2009A\%26A...497..243D} {497, 243}

\makeatother
\end{thebibliography}

% \begin{acknowledgements}
%   \small
%   We are grateful to S.~Torres, M.~C.~Ramirez-Tannus,
%   and C.~J.~Evans for help and discussions. SdM has received funding under the European Unions Horizon 2020 research and innovation programme from the European Research Council (ERC) (Grant agreement No. 715063). VHB acknowledges support from the NRC-Canada Plaskett Fellowship. This work has made use of data from the ESA space mission \emph{Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the \emph{Gaia} Data Processing and Analysis Consortium (DPAC, \url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \emph{Gaia} Multilateral Agreement. % The background image of \Figref{fig:main} is based on observations
%   % made with ESO Telescopes at the La Silla Observatory under programme
%   % ID 076.C-0888, processed and released by the ESO VOS/ADP group.
%   % This research made use of APLpy, an open-source plotting package for Python \citep[][]{robitaille:12}.
% \end{acknowledgements}
